Finding Optimal Sequences for Area Aggregation ---\protect\\ \Astar vs. Integer Linear Programming

### 2019-02-17 area_agg_seq_tsas.tex
test

\begin{document}
\title{Finding Optimal Sequences for Area Aggregation  
	--\protect\\ 
	\Astar vs. Integer Linear Programming}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
%We compared the \Astar algorithm and 
%integer linear programming in solving this problem.
For solving such a problem, standard approaches
are the \Astar algorithm or integer linear programming.
%We compare how the two methods solve our problem.
To avoid long computing times, we allow the two methods to 
return nonoptimal results.
In addition, we present a greedy algorithm 
as a benchmark.
We tested the three methods with a
data set of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

CMG has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area, 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them (e.g., \citealp{Cecconi2003,Noellenburg2008,Chazal2010BallMap,Deng2015,Li2017_Building,Li2017Annealing}).
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} presented a method for computing an optimum
correspondence between two given polylines according to some cost function.
While straight-line trajectories 
are often used for interpolation
(e.g., \citealp{Cecconi2003,Deng2015}),
\textcite{Whited2011BallMorph} considered four other alternatives, i.e., \emph{hat}, \emph{tangent}, 
\emph{circular}, and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\mypar{Optimization in map generalization}
Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land cover areas become too small to be seen.
These areas have to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as good as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{smallest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then we can say that the model is not reasonable.
In this case, we should try another model, say, 
to minimize the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
(e.g., \citealp{HaunertWolff2010AreaAgg,Haunert2016Partition}).
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

@@

We assume that there exist many-to-one relationships between the 
areas of the
start map and the areas of the goal map.
This assumption is based on the fact that many algorithms (e.g., \citealp{HaunertWolff2010AreaAgg,vanSmaalen2003,Oehrlein2017Aggregation})
that aggregate land-cover areas
result in many-to-one relationships.
The input and the generalized results of these methods 
can be used as our input.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its 
components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, with the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single output scale, 
given a land-cover map at a larger scale.
Although the method of \textcite{HaunertWolff2010AreaAgg}
leads to results of high quality, 
it does not yield land-cover maps at intermediate scales.

@@

It is difficult to define exactly what reasonable means 
because users may have different preferences.
Four preferences are discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
They are aggregating a small land-cover area into one 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one is based on semantics and 
the other is based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by human being 
if it is more compact (less clutter).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness:
we consider a subdivision~\Pnode as more compact than
another subdivision~$P_{t,i'}$ if the total length of the interior boundaries of~\Pnode is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
see, for example, \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a reasonable replacement
when compactness is considered in an ILP
(e.g., \citealp{Minas2016,Wright1983}).
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is the centroid
that minimizes the sum.
The sum of the distances can also be computed linearly.
We use the length of interior boundaries 
instead of the distance because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

@@

\emph{Linear programming} is a method 
to optimize a \emph{linear objective}
subject to a set of \emph{linear constraints},
with some \emph{variables}.
For example, suppose that we are selling coffee.
We have~$3.5\,$kg of coffee powder and~$10\,$kg of water.
We mix the powder and the water to provide coffee with 
two kinds of intensity in terms of mass:~$40\%$ and~$20\%$.
The profits of the two kinds of coffee 
are respectively~$5\,$\euro and~$4\,$\euro.
We want to maximize the total profit of selling coffee.
If we offer respectively~$x\,$kg and~$y\,$kg 
of the two kinds of coffee,
then~$x$ and~$y$ are our variables.
Our objective is to
$$
\mathrm{maximize} 	\quad	 5x+4y
$$
To provide~$x\,$kg of coffee with intensity~$40\%$,
we need to use~$0.4x\,$kg of coffee powder 
and~$0.6x\,$kg water.
Analogously, it consumes~$0.2y\,$kg of coffee powder 
and~$0.8y\,$kg of water to produce~$y\,$kg of coffee
with intensity~$20\%$.
Therefore, we have four constraints:
\begin{align*}
0.4x+0.2y	&\le 3.5,				\\
0.6x+0.8y 	&\le 10,	\text{~and}			\\
x,y			&\ge 0.
\end{align*}
With the objective and the constraints, 
we have set up a \emph{linear program} (LP).
We observed that 
all the feasible solutions, i.e., pairs of~$(x,y)$,
fall in the gray area 
shown in \fig\ref{fig:AreaAgg_ILPIllustration}a.
Drawing a line with slope~$-\frac{5}{4}$,
we see that every pair of~$(x,y)$ lying on the line
yields the same result for~$5x+4y$, 
the profit we want to maximize.
For example, every pair of~$(x,y)$ lying on the dashed line
in \fig\ref{fig:AreaAgg_ILPIllustration}a 
yields profit~$40\,$\euro.
If we move the dashed line to the upper right,
then we are able to achieve a larger value for~$5x+4y$. 
In order to maximize the profit, 
we move the dashed line to the upper right as much as possible
and at the same time make sure that 
the it still intersects with the gray area.
Note that if the dashed line 
does not intersect with the gray area,
then there is no feasible pair of~$(x,y)$ 
on the dashed line anymore.
As a result, we get the optimal solution 
when the dashed line hits point~$A$,
where the profit is~$5 \cdot 4 + 4 \cdot 9.5 =58\,$\euro.
\textcite{Karmarkar1984LP}
proved that an LP can be solved in a polynomial time.

Now we change our problem a bit.
We assume that we want to sell coffee in bottles,
where each bottle contains exactly~$1\,$kg of coffee 
with intensity either~$40\%$ or~$20\%$.
Our question becomes how many bottles of each kind of coffee
we should sell in order to maximize the profit.
If we sell the two kinds of coffee 
respectively~$x'$ and~$y'$ bottles,
then our problem becomes:
\begin{alignat*}{3}
&&\text{maximize} 	\quad	&& 5x'+4y' 		&			\\
&&\text{subject to} \quad	&& 0.4x'+0.2y'	&\le 3.5, 	\\
&&					\quad	&& 0.6x'+0.8y' 	&\le 10, 	\\
&&					\quad	&& x', y' 		&\ge 0, 	\\
&&\text{and} 		\quad	&& x', y'		&\in \mathbb{Z}.
\end{alignat*}
For this problem, only the pairs of~$(x,y)$ 
represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
are feasible solutions
(point~$A$ is no longer an optimal solution in this case).
In order to maximize our profit,
we should move the dashed line to the upper right 
as much as possible
and at the same time make sure that 
it hits at least one of the gray dots.
To solve such a problem is known as
\emph{integer linear programming},
which is NP-complete.
Despite the fact, there are
mathematical solvers yielding optimal solutions
for some NP-complete problems in reasonable time
\parencite{Haunert2017Label}.
Also, by using these solvers we profit 
from every improvement, by their producers,
for the same class of problems
\parencite{Haunert2017Label}.
The general form of an \emph{integer linear program} (ILP) is
\begin{alignat*}{3}
&&\text{maximize} 	\quad&& \bm{C}^\mathrm{T}\bm{X}	&		\\
&&\text{subject to} \quad&& \bm{EX}			&\le \bm{H}, 	\\
&&					\quad&& \bm{X} 			&\ge \bm{0}, 	\\
&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I.
\end{alignat*}
where vector~$\bm{X}$ represents integer variables, 
vector~$\bm{C} \in \mathbb{R}^I$, 
vector~$\bm{H} \in \mathbb{R}^J$,
and~$\bm{E}$ is a $(J \times I)$-matrix over the reals.
Furthermore, if we require that
$$
\bm{X} 	\in \{0,1\}^I,
$$
then we have only binary variables for an ILP.
Binary variables are important 
because they occur regularly in optimizations
\parencite[\sect9.2]{bradley1977applied}.
Also, an ILP with general (bounded) integer variables 
can always be translated to an ILP with binary variables
\parencite[\sect2.3]{Williams2009Integer}.
To find optimal sequences for area aggregation, 
we are going to use binary variables in our ILP.

\begin{figure*}[tb]
\centering
\includegraphics[page=4]{AreaAgg_ILP}
\caption{Example of linear programming (a)
	and integer linear programming (b). 
}
\label{fig:AreaAgg_ILPIllustration}
\end{figure*}

@@

\section{Case Study}
\label{sec:AreaAgg_CaseStudy}
We have implemented our methods 
based on C\# (Microsoft Visual Studio~2017) 
and ArcObjects SDK~10.6.0.
We used the IBM ILOG
CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
Our prototype is open access on 
GitHub\footnote{
	\url{https://github.com/IGNF/ContinuousGeneralisation},
	Accessed: Jun 18, 2018.}.
Our computer ran
Windows~10 on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$16\,$GB RAM.
We measured processing time 
by the built-in C\# class \emph{Stopwatch}.
As required by ArcObjects SDK~10.6.0,
we specified our program to run on the~$32$-bit platform. 
We added a post-build task about ``largeaddressaware''
in Microsoft Visual Studio so that 
we were able to use up to~$3\,$GB of main memory\footnote{
	The details of the setting can be found at 	
	\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
	Accessed: Nov 1, 2017.}.
Our CPLEX version may declare an optimal solution
while it is not really optimal.
To fix this problem, we had to disable 
both primal and dual presolve reductions\footnote{
	For more details about the problem, see
	\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
	Accessed: Nov 12, 2017.}.

@@

\begin{figure}[tb]
\captionsetup[subfigure]{labelformat=empty}
\begin{subfigure}[b]{.49\textwidth}
	\centering
	\includegraphics[page=1]{AreaAgg_Data}
	\caption{Start map, $5{,}537$ polygons, \\
		at scale $1:50{,}000$}
\end{subfigure}
\hfill
\begin{subfigure}[b]{.49\textwidth}
	\centering
	\includegraphics[page=2]{AreaAgg_Data}
	\caption{Goal map, $734$ polygons, \\
		at scale $1:250{,}000$}
\end{subfigure}
%
%	\par\vspace{\intextsep} %Leave a gap between the two figures
\par\vspace{\baselineskip} %Leave a gap	figures
%
\begin{subfigure}{\textwidth}
	\centering
	\includegraphics[page=3]{AreaAgg_Data}
	\caption{The 20 land-cover types appearing in our data}
\end{subfigure}
\caption{The data of our case study.}
\label{fig:AreaAgg_Data}
\end{figure}

>>>>

\begin{document}
\title{Finding Optimal Sequences for Area Aggregation  
	---\protect\\ 
	\Astar vs. Integer Linear Programming}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
%We compared the \Astar algorithm and 
%integer linear programming in solving this problem.
For solving such a problem, standard approaches
are the \Astar algorithm or integer linear programming.
%We compare how the two methods solve our problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm 
as a benchmark.
We tested the three methods with a
data set of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

CMG has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area, 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} presented a method for computing an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\mypar{Optimization in map generalization}
Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land cover areas become too small to be seen.
These areas have to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as good as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{smallest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then we can say that the model is not reasonable.
In this case, we should try another model, say, 
to minimize the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

@@

We assume that there exist many-to-one relationships between the 
areas of the
start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
that aggregate land-cover areas
result in many-to-one relationships.
The input and the generalized results of these methods 
can be used as our input.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its 
components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, with the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single output scale, 
given a land-cover map at a larger scale.
Although the method of \textcite{HaunertWolff2010AreaAgg}
leads to results of high quality, 
it does not yield land-cover maps at intermediate scales.

@@

It is difficult to define exactly what reasonable means 
because users may have different preferences.
Four preferences are discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
They are aggregating a small land-cover area into one 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one based on semantics and 
the other based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by human being 
if it is more compact (less clutter).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness:
we consider a subdivision~\Pnode as more compact than
another subdivision~$P_{t,i'}$ 
if the total length of the interior boundaries of~\Pnode 
is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
see, for example, \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a reasonable replacement
when compactness is considered in an ILP
\parencite[e.g.,][]{Minas2016,Wright1983}.
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is the centroid
that minimizes the sum.
The sum of the distances can also be computed linearly.
We use the length of interior boundaries 
instead of the distance because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

@@

\emph{Linear programming} is a method 
to optimize a \emph{linear objective}
subject to a set of \emph{linear constraints},
with some \emph{variables}.
For example, suppose that we are selling coffee.
We have~$3.5\,$kg of coffee powder and~$10\,$kg of water.
We mix the powder and the water to provide two kinds coffee 
with different intensities in terms of mass:~$40\%$ and~$20\%$.
The profits of the two kinds of coffee 
are respectively~$5\,$\euro~and~$4\,$\euro.
Our aim is to maximize the total profit of selling coffee.
If we offer respectively~$x\,$kg and~$y\,$kg 
of the two kinds of coffee,
then~$x$ and~$y$ are our variables.
Our objective is to
$$
\mathrm{maximize} 	\quad	 5x+4y
$$
To provide~$x\,$kg of coffee with intensity~$40\%$,
we need to use~$0.4x\,$kg of coffee powder 
and~$0.6x\,$kg water.
Analogously, it consumes~$0.2y\,$kg of coffee powder 
and~$0.8y\,$kg of water to produce~$y\,$kg of coffee
with intensity~$20\%$.
Therefore, we have four constraints:
\begin{align*}
0.4x+0.2y	&\le 3.5,				\\
0.6x+0.8y 	&\le 10,	\text{~and}			\\
x,y			&\ge 0.
\end{align*}
With the objective and the constraints, 
we have set up a \emph{linear program} (LP).
We observed that 
all the feasible solutions, i.e., pairs of~$(x,y)$,
fall in the gray area 
shown in \fig\ref{fig:AreaAgg_ILPIllustration}a.
Drawing a line with slope~$-\frac{5}{4}$,
we see that every pair of~$(x,y)$ lying on the line
yields the same result for~$5x+4y$, 
the profit we want to maximize.
For example, every pair of~$(x,y)$ lying on the dashed line
in \fig\ref{fig:AreaAgg_ILPIllustration}a 
yields profit~$40\,$\euro.
If we move the dashed line to the upper right,
then we are able to achieve a larger value for~$5x+4y$. 
In order to maximize the profit, 
we move the dashed line to the upper right as much as possible
and at the same time make sure that 
it still intersects with the gray area.
Note that if the dashed line 
does not intersect with the gray area,
then there is no feasible pair of~$(x,y)$ 
on the dashed line anymore.
As a result, we get the optimal solution 
when the dashed line hits point~$A$,
where the profit is~$5 \cdot 4 + 4 \cdot 9.5 =58\,$\euro.
\textcite{Karmarkar1984LP}
proved that an LP can be solved in polynomial time.

Now we change our problem a bit.
We wish to sell coffee in jugs,
where each jug contains exactly~$1\,$kg of coffee 
with intensity~$40\%$ or~$20\%$.
Our question becomes how many jugs of each kind of coffee
we should sell in order to maximize the profit.
If we sell the two kinds of coffee 
respectively~$x'$ and~$y'$ jugs,
then our problem becomes:
\begin{alignat*}{3}
&&\text{maximize} 	\quad	&& 5x'+4y' 		&			\\
&&\text{subject to} \quad	&& 0.4x'+0.2y'	&\le 3.5, 	\\
&&					\quad	&& 0.6x'+0.8y' 	&\le 10, 	\\
&&					\quad	&& x', y' 		&\ge 0, 	\\
&&\text{and} 		\quad	&& x', y'		&\in \mathbb{Z}.
\end{alignat*}
For this problem, only the pairs of~$(x',y')$ 
represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
are feasible solutions
(point~$A$ is no longer a solution in this case).
In order to maximize our profit,
we should move the dashed line to the upper right 
as much as possible
and at the same time make sure that 
it hits at least one of the gray dots.
To solve such a problem is known as
\emph{integer linear programming},
which is NP-complete.
Despite the fact, there are
mathematical solvers yielding optimal solutions
for some NP-complete problems in reasonable time
\parencite{Haunert2017Label}.
Also, by using these solvers we benefit 
from every improvement, by their producers,
for the same class of problems
\parencite{Haunert2017Label}.
The general form of an \emph{integer linear program} (ILP) is
\begin{alignat*}{3}
&&\text{maximize} 	\quad&& \bm{C}^\mathrm{T}\bm{X}	&		\\
&&\text{subject to} \quad&& \bm{EX}			&\le \bm{H}, 	\\
&&					\quad&& \bm{X} 			&\ge \bm{0}, 	\\
&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I.
\end{alignat*}
where vector~$\bm{X}$ represents integer variables, 
vector~$\bm{C} \in \mathbb{R}^I$, 
vector~$\bm{H} \in \mathbb{R}^J$,
and~$\bm{E}$ is a $(J \times I)$-matrix over the reals.
Furthermore, if we require that
$$
\bm{X} 	\in \{0,1\}^I,
$$
then we have only binary variables for an ILP.
Binary variables are important 
because they occur regularly in optimizations
\parencite[\sect9.2]{bradley1977applied}.
Also, an ILP with general (bounded) integer variables 
can always be translated to an ILP with binary variables
\parencite[\sect2.3]{Williams2009Integer}.
To find optimal sequences for area aggregation, 
we are going to use binary variables in our ILP.

\begin{figure*}[tb]
\centering
\includegraphics[page=4]{AreaAgg_ILP}
\caption{Examples of linear programming (a)
	and integer linear programming (b). 
}
\label{fig:AreaAgg_ILPIllustration}
\end{figure*}

@@

\section{Case Study}
\label{sec:AreaAgg_CaseStudy}
We have implemented our methods 
based on C\# (Microsoft Visual Studio~2017) 
and ArcObjects SDK~10.6.0.
We used the IBM ILOG
CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
Our prototype is open access on 
GitHub\footnote{
	\url{https://github.com/IGNF/ContinuousGeneralisation},
	Accessed: Jun 18, 2018.}.
We ran our case study
under 64-bit Windows~10 
on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$4$ cores;
the computer has $16\,$GB RAM.
We measured processing time 
by the built-in C\# class \emph{Stopwatch}.
As required by ArcObjects SDK~10.6.0,
we specified our program to run on the~$32$-bit platform. 
We added a post-build task about ``largeaddressaware''
in Microsoft Visual Studio so that 
we were able to use up to~$3\,$GB of main memory\footnote{
	The details of the setting can be found at 	
	\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
	Accessed: Nov 1, 2017.}.
Our CPLEX version may declare an optimal solution
while it is not really optimal.
To fix this problem, we had to disable 
both primal and dual presolve reductions\footnote{
	For more details about the problem, see
	\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
	Accessed: Nov 12, 2017.}.

@@

\begin{figure}[tb]
\captionsetup[subfigure]{labelformat=empty}
\begin{subfigure}[b]{.49\textwidth}
	\centering
	\includegraphics[page=1]{AreaAgg_Data}
	\caption{Start map, $5{,}537$ polygons, \\
		at scale $1:50{,}000$}
\end{subfigure}
\hfill
\begin{subfigure}[b]{.49\textwidth}
	\centering
	\includegraphics[page=2]{AreaAgg_Data}
	\caption{Goal map, $734$ polygons, \\
		at scale $1:250{,}000$}
\end{subfigure}
%
%It doesn't work to directly use 
%\vspace{\baselineskip} for subfigures.
\par\vspace{\baselineskip} %Leave a gap	figures
%
\begin{subfigure}{\textwidth}
	\centering
	\includegraphics[page=3]{AreaAgg_Data}
	\caption{The 20 land-cover types appearing in our data}
\end{subfigure}
\caption{The data of our case study.}
\label{fig:AreaAgg_Data}
\end{figure}
